Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-02-17 manuscript/appendix.Rmd
added figures to SI
issue #59

header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}
                  \captionsetup[table]{labelformat=empty}
                  \captionsetup[figure]{labelformat=empty}
---

@@

>>>>

header-includes:  \usepackage{float}
                  \usepackage[font=normalsize,format=plain,justification=raggedright, labelformat=empty]{caption}
---

@@

\newpage
![Figure S3. Ratios among FACF as a function of latitude and climate variables](tables_figures/ratio_grid_plots.png)

\newpage
![Figure S4. Individual plots of FACF in relation to mean annual climate, part 1.](tables_figures/grid_plots_climate1.png)

\newpage
![Figure S5. Individual plots of FACF in relation to mean annual climate, part 2.](tables_figures/grid_plots_climate2.png)

\newpage
![Figure S6. Individual plots of FACF in relation to mean climate seasonality, part 1.](tables_figures/grid_plots_seasonality3.png)

\newpage
![Figure S7. Individual plots of FACF in relation to mean climate seasonality, part 2.](tables_figures/grid_plots_seasonality4.png)

\newpage
![Figure S8. Growing season length-standardized FACF in relation to mean growing season climate, part 1.](tables_figures/gridded_growing_season1.png)

\newpage
![Figure S9. Growing season length-standardized FACF in relation to mean growing season climate, part 2.](tables_figures/gridded_growing_season2.png)
